```{r}
claims_data <- read.csv("C:/Users/zz012/Downloads/UNSW_claims_data.csv",header = TRUE)
earned_data <- read.csv("C:/Users/zz012/Downloads/UNSW_earned_data_adjusted_Sep27.csv",header = TRUE)
forecast_data<-read.csv("C:/Users/zz012/Downloads/New_Customers_Pricing_Output_File.csv",header = TRUE)
```
```{r}
library(truncnorm)
library(boot)
library(dplyr)
library(tidyr)
library(glmnet)
library(forcats)
library(gbm)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(pscl)
library(MASS)
```
***STEP1 DATA CLEANING AND PROCESSING***

*1.delete the negative tenure rows in claims and earned*
*2.delete claims with zero total claim amount*
*3.order the data based on exposure id and tenure add missing value as NA, check the data*
*4. change missing owner age to the average and missing breed trait to "unknown",merge two data based on exposure id and tenure keep useful columns for following exploration(delete initial row number X, suburb name, policyholders' date of birth, extra breed name selected, duplicate exposure id, row number)*
*4. add dummy variables for each category and prepare to fit a series of poisson with lasso regularization*

```{r}
earned_data <- earned_data %>%
  filter(tenure >= 0)
claims_data <- claims_data %>%
  filter(tenure>= 0)
claims_data <- claims_data %>%
  filter(total_claim_amount > 0)
sorted_df1 <- earned_data %>%
    arrange(exposure_id, tenure)
sorted_df2 <-claims_data %>%
    arrange(exposure_id,tenure)
sorted_df1[sorted_df1 == ""] <- NA
sorted_df2[sorted_df2 == ""] <- NA
mean_age <- mean(sorted_df1$owner_age_years, na.rm = TRUE)
sorted_df1 <- sorted_df1 %>%
  mutate( owner_age_years= ifelse(is.na(owner_age_years), mean_age, owner_age_years))
sorted_df1 <- sorted_df1 %>%
  mutate(nb_breed_trait = ifelse(is.na(nb_breed_trait), "unknown", nb_breed_trait))
sorted_df1 <- sorted_df1 %>%
    mutate(pet_is_switcher = ifelse(is.na(pet_is_switcher), "unknown", pet_is_switcher))
earned_with_claim_info <- sorted_df1 %>%
  left_join(sorted_df2 %>% 
              dplyr::select(exposure_id,tenure,condition_category, claim_paid, total_claim_amount,claim_start_date)  %>% mutate(claim_happened = 1),
            by = c("exposure_id", "tenure"))
earned_with_claim_info <- earned_with_claim_info[,-c(1,14,17,26,31,32)]
earned_with_claim_info <-earned_with_claim_info %>%
  mutate( condition_category= ifelse(is.na(condition_category), "NA", condition_category))

dummy_vars <- model.matrix(~ condition_category - 1, data = earned_with_claim_info)
earned_with_claim_info2<-cbind(earned_with_claim_info,dummy_vars)
earned_with_claim_info2<-earned_with_claim_info2[,-41]
# Now you can group and summarize
claims_per_exposure2 <- earned_with_claim_info2 %>%
  group_by(exposure_id,tenure) %>%
  summarize(
    claim_count = sum(claim_happened, na.rm = TRUE),                # Count number of claims
    avg_claim_amount = mean(total_claim_amount[claim_happened == 1], na.rm = TRUE),  # Average claim size for claims that happened
  )
claims_per_exposure <- earned_with_claim_info2 %>%
  group_by(exposure_id, tenure) %>%
  summarize(
   across(c(31:41),~ sum(., na.rm = TRUE), .names = "{.col}_count"),  # Count how many claims in each specified column
 across(c(31:41), ~ mean(total_claim_amount[. == 1], na.rm = TRUE), .names = "{.col}_average_claim") ,
  ) %>%
  ungroup()
earned_with_claim_info2 <- sorted_df1 %>%
  left_join(claims_per_exposure, by = c("exposure_id", "tenure"))%>%
  left_join(claims_per_exposure2, by = c("exposure_id", "tenure"))
earned_with_claim_info2 <- earned_with_claim_info2 %>%
  mutate(de_sex_condition = ifelse(pet_de_sexed == "false", "no", pet_de_sexed_age))
earned_with_claim_info2$UW_Date <- as.POSIXct( earned_with_claim_info2$UW_Date, format = "%Y-%m-%d %H:%M:%S")
 earned_with_claim_info2$months <- format(earned_with_claim_info2$UW_Date, "%m") 
earned_with_claim_info2 <- earned_with_claim_info2 %>%
  mutate(de_sex_condition = recode(de_sex_condition,
                                   "0-3 months" = "0-3 mo",
                                   "7-12 months" = "7-12 mo",
                                   "1-2 years" = "1-2 yr",
                                   "2+ years" = "2+ yr"))
earned_with_claim_info2 <- earned_with_claim_info2 %>%
  mutate(pet_age_month_updating = tenure + pet_age_months)

```
```{r}
earned_with_claim_info2[, c(5, 8, 13, 16, 18, 23, 24,25,27,59,58 )] <- 
  lapply(earned_with_claim_info2[, c(5, 8, 13, 16,18, 23, 24,25,27,59,58)], as.factor)
earned_with_claim_info2<-earned_with_claim_info2%>%
  filter(earned_units>0.01)
earned_with_claim_info2 <- earned_with_claim_info2 %>%
  mutate(nb_breed_name_unique = fct_lump_min(nb_breed_name_unique, min = 50))
earned_with_claim_info3<-earned_with_claim_info2%>%
    filter(avg_claim_amount!="NaN")
names_less_than_50 <- earned_with_claim_info2 %>%
  group_by(nb_breed_name_unique) %>%
  summarise(count = n()) %>%
  filter(count < 50) %>%
  pull(nb_breed_name_unique)
```
```{r}
forecast_data2 <- forecast_data[!forecast_data$nb_breed_trait %in% c('siamese', 'forest cat', 'spotted cats', 'persian', 'burmese'), ]
forecast_data2[forecast_data2 == ""] <- NA
forecast_data2 <-forecast_data2 %>%
  mutate_all(~ ifelse(. == "FALSE", "false", .))%>%
  mutate_all(~ ifelse(. == "TRUE", "true", .))
forecast_data2<- forecast_data2 %>%
  mutate( owner_age_years= ifelse(is.na(owner_age_years), mean_age, owner_age_years))
forecast_data2 <- forecast_data2 %>%
  mutate(nb_breed_trait = ifelse(is.na(nb_breed_trait), "unknown", nb_breed_trait))
forecast_data2 <- forecast_data2 %>%
    mutate(pet_is_switcher = ifelse(is.na(pet_is_switcher), "unknown", pet_is_switcher))
forecast_data2 <- forecast_data2 %>%
  mutate(de_sex_condition = ifelse(pet_de_sexed == "false", "no", pet_de_sexed_age))
forecast_data2 <- forecast_data2 %>%
  mutate(de_sex_condition = recode(de_sex_condition,
                                   "0-3 months" = "0-3 mo",
                                   "7-12 months" = "7-12 mo",
                                   "1-2 years" = "1-2 yr",
                                   "2+ years" = "2+ yr"))
forecast_data2$earned_units<-1
forecast_data2 <- forecast_data2 %>%
  mutate(nb_breed_name_unique = ifelse(nb_breed_name_unique %in% names_less_than_50, "Other", nb_breed_name_unique))
names(forecast_data2)[6] <- c("pet_age_month_updating")
forecast_data2[, c(2,5, 9, 12, 14, 19, 20, 21,23,28 )] <- 
  lapply(forecast_data2[, c(2,5, 9, 12, 14, 19, 20, 21,23,28 )], as.factor)
training_levels <- levels(factor(earned_with_claim_info2$nb_breed_name_unique))
forecast_data2$nb_breed_name_unique <- fct_other(forecast_data2$nb_breed_name_unique, keep = training_levels, other_level = "Other")
x_final_1 <- model.matrix( ~de_sex_condition+is_multi_pet_plan+ nb_breed_trait+
  nb_breed_name_unique+ 
  nb_breed_type+ 
  nb_number_of_breeds+
  owner_age_years+ 
  nb_state+ 
  nb_address_type_adj+ 
  pet_is_switcher+ 
  pet_gender+ 
  pet_age_month_updating+ 
  nb_average_breed_size+
  nb_contribution_excess+earned_units , data = forecast_data2)
x_final_2<-model.matrix( ~de_sex_condition+is_multi_pet_plan+ nb_breed_trait+
  nb_breed_name_unique+ 
  nb_breed_type+ 
  nb_number_of_breeds+
  owner_age_years+ 
  nb_state+ 
  nb_address_type_adj+ 
  pet_is_switcher+ 
  pet_gender+ 
  pet_age_month_updating+ 
  nb_average_breed_size+
  nb_contribution_excess , data = forecast_data2)
```
***STEP1.5 FIGURE OUT HOW TO GET THE CLAIM_PAID KNOWING TOTAL_CLAIM_AMOUNT***

```{r}
earned_with_claim_info_cal <- earned_with_claim_info %>%
  group_by(exposure_id, condition_category) %>%
  arrange(claim_start_date)%>%
  
  # Step 1: Identify the occurrence (first, second, etc.)
  mutate(occurrence = row_number()) %>%
  mutate(paid = ifelse(occurrence == 1,
                      ifelse(total_claim_amount > nb_excess,0.92*(total_claim_amount - nb_excess / 1.1) * nb_contribution / 100,0),0))%>%
  mutate(previous_paid=0)
  for (i in 2:max(earned_with_claim_info_cal$occurrence)) {
earned_with_claim_info_cal<- earned_with_claim_info_cal%>%
  mutate(previous_paid = ifelse(occurrence == i,cummax(paid),previous_paid))%>% 
  mutate(paid = ifelse(occurrence == i,
                      ifelse(total_claim_amount > nb_excess,
                             ifelse(previous_paid > 0,0.92*total_claim_amount * nb_contribution / 100,0.92*(total_claim_amount - nb_excess / 1.1) * nb_contribution / 100),paid),paid))}
  earned_with_claim_info_cal$paid_erro<-earned_with_claim_info_cal$paid-earned_with_claim_info_cal$claim_paid
 earned_with_claim_info_cal<-filter(earned_with_claim_info_cal,paid_erro!="NA")
  summary(earned_with_claim_info_cal$paid_erro)
  qqnorm(earned_with_claim_info_cal$paid_erro)
qqline(earned_with_claim_info_cal$paid_erro, col = "red")
#delete the outlier
earned_with_claim_info_cal<-earned_with_claim_info_cal[earned_with_claim_info_cal$paid_erro<2000,]
earned_with_claim_info_cal<-earned_with_claim_info_cal[earned_with_claim_info_cal$paid_erro>-2000,]
qqnorm(earned_with_claim_info_cal$paid_erro)
qqline(earned_with_claim_info_cal$paid_erro, col = "red")
```

```{r}
x_test_1 <- model.matrix(claim_count ~de_sex_condition+is_multi_pet_plan+ nb_breed_trait+
  nb_breed_name_unique+ 
  nb_breed_type+ 
  nb_number_of_breeds+
  owner_age_years+ 
  nb_state+ 
  nb_address_type_adj+ 
  pet_is_switcher+ 
  pet_gender+ 
  pet_age_month_updating+ 
  nb_average_breed_size+
  nb_contribution_excess+earned_units , data = earned_with_claim_info2)
x_test <- model.matrix(claim_count ~de_sex_condition+is_multi_pet_plan+ nb_breed_trait+
  nb_breed_name_unique+ 
  nb_breed_type+ 
  nb_number_of_breeds+
  owner_age_years+ 
  nb_state+ 
  nb_address_type_adj+ 
  pet_is_switcher+ 
  pet_gender+ 
  pet_age_month_updating+ 
  nb_average_breed_size+
  nb_contribution_excess , data = earned_with_claim_info2)
```
***STEP2 FIT MODELS IN BOTH FREQUENCY AND SEVERITY***
```{r}
response_vars_sev <- c("condition_categoryAllergies & skin_average_claim", "condition_categoryBehavioral Issues_average_claim","condition_categoryDental_average_claim","condition_categoryEyes & ears_average_claim","condition_categoryGastrointestinal Issues_average_claim","condition_categoryIllness_average_claim","condition_categoryIngestion_average_claim","condition_categoryInjuries_average_claim","condition_categoryOrtho_average_claim","condition_categoryOther_average_claim","condition_categoryRoutine Care and Examinations_average_claim","avg_claim_amount")
predictor_formula_sev <- ~ de_sex_condition + is_multi_pet_plan + nb_breed_trait +
  nb_breed_name_unique + nb_breed_type + nb_number_of_breeds +
  owner_age_years + nb_state + nb_address_type_adj +
  pet_is_switcher + pet_gender + pet_age_month_updating +
  nb_average_breed_size + nb_contribution_excess
x_list_sev <- list()
y_list_sev <- list()
for (response_var in response_vars_sev) {
    y <- earned_with_claim_info3[[response_var]]
    y <- y[!is.na(y)]
    y_list_sev[[response_var]] <- y  # Store y in the list with the response variable name
    # Filter data to remove rows with NA in the response variable
    data_filtered <- earned_with_claim_info3[!is.na(earned_with_claim_info3[[response_var]]), ]
    x_list_sev[[response_var]] <- model.matrix(predictor_formula_sev, data = data_filtered)  # Store x in the list with the response variable name
  }
```
```{r}
model_list_sev <- list()
cv_sev_errors <- list()
predict_sev <- list()
# Loop over each pair of x and y in the lists
for (i in seq_along(x_list_sev)) {
  # Extract the x and y for this iteration
  y <- y_list_sev[[i]]
  x <- x_list_sev[[i]]
  cv_sev_model <- cv.glmnet(x, y, family = "gaussian", alpha = 1, nfolds = 10) 
  # Fit a Poisson glmnet model
  sev_model <- glmnet(x, y, family = "gaussian", alpha = 1,lambda = cv_sev_model$lambda.min)
  cv_sev_errors[[names(y_list_sev)[i]]] <- cv_sev_model$cvm
 sev_prediction <- predict(sev_model,newx = x_test,type="response")
  model_list_sev[[names(y_list_sev)[i]]] <- sev_model
  predict_sev[[names(y_list_sev)[i]]]<-  sev_prediction
}

```
```{r}
response_vars_fre <- c("condition_categoryAllergies & skin_count", "condition_categoryBehavioral Issues_count","condition_categoryDental_count","condition_categoryEyes & ears_count","condition_categoryGastrointestinal Issues_count","condition_categoryIllness_count","condition_categoryIngestion_count","condition_categoryInjuries_count","condition_categoryOrtho_count","condition_categoryOther_count","condition_categoryRoutine Care and Examinations_count","claim_count")
predictor_formula_fre <- ~ de_sex_condition + is_multi_pet_plan + nb_breed_trait +
  nb_breed_name_unique + nb_breed_type + nb_number_of_breeds +
  owner_age_years + nb_state + nb_address_type_adj +
  pet_is_switcher + pet_gender + pet_age_month_updating +
  nb_average_breed_size + nb_contribution_excess+earned_units
 x <- model.matrix(predictor_formula_fre, data = earned_with_claim_info2)
y_list_fre <- list()
for (response_var in response_vars_fre) {
    y <- earned_with_claim_info2[[response_var]]
    y_list_fre[[response_var]] <- y  # Store y in the list with the response variable name
  }
```
```{r}
model_list_fre <- list()
cv_fre_errors <- list()
cv_fre_minlambda <- list()
predict_fre <- list()
# Loop over each pair of x and y in the lists
for (i in seq_along(y_list_fre)) {
  # Extract the x and y for this iteration
  y <- y_list_fre[[i]]
  cv_fre_model <- cv.glmnet(x, y, family = "poisson", alpha = 1, nfolds = 10) 
  # Fit a Poisson glmnet model
  fre_model <- glmnet(x, y, family = "poisson", alpha = 1,lambda = cv_fre_model$lambda.min)
  cv_fre_errors[[names(y_list_fre)[i]]] <- cv_fre_model$cvm
  cv_fre_minlambda[[names(y_list_fre)[i]]] <- cv_fre_model$lambda.min
  # Store the fitted model in model_list with the name of the response variable
  model_list_fre[[names(y_list_fre)[i]]] <- fre_model
  fre_prediction <- predict(fre_model, newx=x_test_1)
  predict_fre[[names(y_list_fre)[i]]]<-  fre_prediction
}
exp_list_fre <- lapply(predict_fre, exp)
total_claim_individual<-mapply("*",exp_list_fre[1:11],predict_sev[1:11])
row_sum_vector <- rowSums(total_claim_individual)
sum(row_sum_vector)
total_claim_sum<-mapply("*",exp_list_fre[12],predict_sev[12])
sum(total_claim_sum)
trueprice<-sum(earned_with_claim_info3$claim_count*earned_with_claim_info3$avg_claim_amount)
print(trueprice)
mu_hat <- predict(model_list_fre[[12]], newx=x_test_1, type = "response")
# Calculate the log-likelihood for Poisson
log_likelihood <- sum(earned_with_claim_info2$claim_count * log(mu_hat) - mu_hat - lfactorial(earned_with_claim_info2$claim_count))
# Calculate the effective number of parameters (including intercept)
coefficients <- coef(model_list_fre[[12]])
k <- sum(coefficients != 0)

# Calculate AIC
aic <- -2 * log_likelihood + 2 * k
print(aic)
```

```{r}
initial_model_lnorm <- glm(log(avg_claim_amount) ~ 1, data = earned_with_claim_info3, family = gaussian())
full_model_lnorm <- glm(log(avg_claim_amount) ~de_sex_condition+is_multi_pet_plan+ nb_breed_trait+
  nb_breed_name_unique+ 
  nb_breed_type+ 
  nb_number_of_breeds+
  owner_age_years+ 
  nb_state+ 
  nb_address_type_adj+ 
  pet_is_switcher+ 
  pet_gender+ 
  pet_age_month_updating+ 
  nb_average_breed_size+
  nb_contribution_excess , data = earned_with_claim_info3 , family = gaussian())

# Forward Stepwise Selection
step_model_lnorm <- stepAIC(initial_model_lnorm, 
                      scope = list(lower = initial_model_lnorm, upper = full_model_lnorm),
                      direction = "forward")

# Summary of the selected model
summary(step_model_lnorm)
```
```{r}
initial_model_gamma <- glm(avg_claim_amount ~ 1, data = earned_with_claim_info3, family =  Gamma(link = "log"))
full_model_gamma <- glm(avg_claim_amount ~de_sex_condition+is_multi_pet_plan+ nb_breed_trait+
  nb_breed_name_unique+ 
  nb_breed_type+ 
  nb_number_of_breeds+
  owner_age_years+ 
  nb_state+ 
  nb_address_type_adj+ 
  pet_is_switcher+ 
  pet_gender+ 
  pet_age_month_updating+ 
  nb_average_breed_size+
  nb_contribution_excess , data = earned_with_claim_info3 , family =  Gamma(link = "log"))

# Forward Stepwise Selection
step_model_gamma <- stepAIC(initial_model_gamma, 
                      scope = list(lower = initial_model_gamma, upper = full_model_gamma),
                      direction = "forward")

# Summary of the selected model
summary(step_model_gamma)
```
```{r}
initial_model_norm <- glm(avg_claim_amount ~ 1, data = earned_with_claim_info3, family = gaussian())
full_model_norm <- glm(avg_claim_amount ~de_sex_condition+is_multi_pet_plan+ nb_breed_trait+
  nb_breed_name_unique+ 
  nb_breed_type+ 
  nb_number_of_breeds+
  owner_age_years+ 
  nb_state+ 
  nb_address_type_adj+ 
  pet_is_switcher+ 
  pet_gender+ 
  pet_age_month_updating+ 
  nb_average_breed_size+
  nb_contribution_excess , data = earned_with_claim_info3 , family = gaussian())

# Forward Stepwise Selection
step_model_norm <- stepAIC(initial_model_norm, 
                      scope = list(lower = initial_model_norm, upper = full_model_norm),
                      direction = "forward")

# Summary of the selected model
summary(step_model_norm)
```

```{r}
earned_with_claim_info4 <- earned_with_claim_info3 %>%
  mutate(nb_breed_trait = fct_lump_min(nb_breed_trait, min = 10))
set.seed(234)
train_val_shuffle <- earned_with_claim_info4[sample(1:nrow(earned_with_claim_info4)), ]
k <- 5
fold_size <- floor(nrow(earned_with_claim_info4) / k)
mse_lnorm <- numeric(k)
mse_gamma <- numeric(k)
mse_norm<- numeric(k)
for (i in 1:k) {
  val_indices <- ((i - 1) * fold_size + 1):(i * fold_size)
  val <- train_val_shuffle[val_indices, ]
  train <- train_val_shuffle[-val_indices, ] 
  model_lnorm<-glm(formula = log(avg_claim_amount) ~ nb_contribution_excess + 
    nb_breed_trait + nb_number_of_breeds + pet_is_switcher + 
    pet_age_month_updating + nb_breed_type, family = gaussian(), 
    data = train)
  model_gamma<-glm(formula = avg_claim_amount ~ nb_contribution_excess + pet_age_month_updating, 
    family = Gamma(link = "log"), data = train)
 model_norm<- glm(formula = avg_claim_amount ~ nb_contribution_excess + pet_age_month_updating, 
    family = gaussian(), data = train)
  mse_norm[i] <- mean((predict(model_norm, newdata = val) - val$avg_claim_amount)^2)
  mse_lnorm[i] <- mean((predict(model_lnorm, newdata = val) - val$avg_claim_amount)^2)
  mse_gamma[i] <- mean((predict(model_gamma, newdata = val) - val$avg_claim_amount)^2)
}
mse_norm
mse_lnorm
mse_gamma
c(mean(mse_lnorm), mean(mse_gamma),mean(mse_norm))
```
```{r}
gbm_model <- gbm(
  formula = avg_claim_amount ~de_sex_condition+is_multi_pet_plan+ nb_breed_trait+
  nb_breed_name_unique+ 
  nb_breed_type+ 
  nb_number_of_breeds+
  owner_age_years+ 
  nb_state+ 
  nb_address_type_adj+ 
  pet_is_switcher+ 
  pet_gender+ 
  pet_age_month_updating+ 
  nb_average_breed_size+
  nb_contribution_excess ,         # Target variable and predictors
  distribution = "gaussian",  # For regression
  data = earned_with_claim_info3,                # Data frame
  n.trees = 1000,             # Number of trees
  interaction.depth = 3,      # Tree depth
  shrinkage = 0.01,           # Learning rate
  n.minobsinnode = 10,        # Minimum observations in nodes
  cv.folds = 5,               # Number of cross-validation folds
  verbose = TRUE              # Print progress
)
severity<- predict(gbm_model,newdata =earned_with_claim_info2 )
sum(exp_list[[12]]*severity)
```
```{r}
mu<-mean(earned_with_claim_info2$claim_count)
sigma2<-var(earned_with_claim_info2$claim_count)
print(mu)
print(sigma2)
```
```{r}
initial_model_p <- glm(claim_count ~ 1, data = earned_with_claim_info2, family = poisson(link = "log"))
full_model_p <- glm(claim_count ~de_sex_condition+is_multi_pet_plan+ nb_breed_trait+
  nb_breed_name_unique+ 
  nb_breed_type+ 
  nb_number_of_breeds+
  owner_age_years+ 
  nb_state+ 
  nb_address_type_adj+ 
  pet_is_switcher+ 
  pet_gender+ 
  pet_age_month_updating+ 
  nb_average_breed_size+
  nb_contribution_excess+earned_units , data = earned_with_claim_info2 , family = poisson(link = "log"))

# Forward Stepwise Selection
step_model_p <- stepAIC(initial_model_p, 
                      scope = list(lower = initial_model_p, upper = full_model_p),
                      direction = "forward")

# Summary of the selected model
summary(step_model_p)
```
```{r}
initial_model_nb <- glm.nb(claim_count ~ 1, data = earned_with_claim_info2)
full_model_nb <- glm.nb(claim_count ~de_sex_condition+is_multi_pet_plan+ nb_breed_trait+
  nb_breed_name_unique+ 
  nb_breed_type+ 
  nb_number_of_breeds+
  owner_age_years+ 
  nb_state+ 
  nb_address_type_adj+ 
  pet_is_switcher+ 
  pet_gender+ 
  pet_age_month_updating+ 
  nb_average_breed_size+
  nb_contribution_excess+earned_units , data = earned_with_claim_info2 )

# Forward Stepwise Selection
step_model_nb <- stepAIC(initial_model_nb, 
                      scope = list(lower = initial_model_nb, upper = full_model_nb),
                      direction = "forward")

# Summary of the selected model
summary(step_model_nb)
```
```{r}
vuong(step_model_p, step_model_nb)

```
```{r}
mu_hat <- predict(step_model_nb, type = "response")
lambda_hat <- predict(step_model_p, type = "response")
theta <- 1 / step_model_nb$theta 
claim_0 <- sum(earned_with_claim_info2$claim_count == 0)
claim_1 <- sum(earned_with_claim_info2$claim_count == 1)
claim_2 <- sum(earned_with_claim_info2$claim_count == 2)
claim_3 <- sum(earned_with_claim_info2$claim_count == 3)
claim_4 <- sum(earned_with_claim_info2$claim_count == 4)
claim_5 <- sum(earned_with_claim_info2$claim_count == 5)
E_nb_0 <- sum(dnbinom(0, size = theta, mu = mu_hat))
E_nb_1 <- sum(dnbinom(1, size = theta, mu = mu_hat))  
E_nb_2 <- sum(dnbinom(2, size = theta, mu = mu_hat)) 
E_nb_3 <- sum(dnbinom(3, size = theta, mu = mu_hat)) 
E_nb_4 <- sum(dnbinom(4, size = theta, mu = mu_hat))
E_nb_5 <- sum(dnbinom(5, size = theta, mu = mu_hat))
E_p_0 <- sum(dpois(0, lambda = lambda_hat))
E_p_1 <- sum(dpois(1, lambda = lambda_hat))  
E_p_2 <- sum(dpois(2, lambda = lambda_hat))  
E_p_3 <- sum(dpois(3, lambda = lambda_hat))
E_p_4 <- sum(dpois(4, lambda = lambda_hat))
E_p_5 <- sum(dpois(5, lambda = lambda_hat))
NB<-c(E_nb_0,E_nb_1,E_nb_2,E_nb_3,E_nb_4,E_nb_5)
names(NB) <- c("y = 0", "y = 1", "y = 2", "y = 3","y = 4","y = 5")
POI<-c(E_p_0,E_p_1,E_p_2,E_p_3,E_p_4,E_p_5)
names(POI) <- c("y = 0", "y = 1", "y = 2", "y = 3","y = 4","y = 5")
Real_data<-c(claim_0,claim_1,claim_2,claim_3,claim_4,claim_5)
names(POI) <- c("y = 0", "y = 1", "y = 2", "y = 3","y = 4","y = 5")
E_table <- data.frame(NB,POI,Real_data) 
E_table$NB <- format(E_nb_table$NB, scientific = FALSE, digits = 5)
E_table$POI <- format(E_p_table$POI, scientific = FALSE, digits = 5)

print(E_table)
```
```{r}
fre_nb<-predict(step_model_nb,newdata = earned_with_claim_info2,type = "response")
estimateprice<-sum(fre_nb*predict_sev[[12]])
print(estimateprice)
```
***STEP3 FINAL PREDICTION***
```{r}
lambda0<-predict(model_list_fre[[12]],newx=x_final_1,type="response")
E_p_0 <- dpois(0, lambda = lambda0)
E_p_1 <- dpois(1, lambda = lambda0)  
E_p_2 <- dpois(2, lambda = lambda0)  
set.seed(123)
random_amounts_1 <- rlnorm(nrow(forecast_data2), meanlog = log(mean(earned_with_claim_info3$avg_claim_amount)), sdlog = sd(log(earned_with_claim_info3$avg_claim_amount)))
random_amounts_2 <- rlnorm(nrow(forecast_data2), meanlog = log(mean(earned_with_claim_info3$avg_claim_amount)), sdlog = sd(log(earned_with_claim_info3$avg_claim_amount)))
forecast_data2$e_values<-0
for (i in 1:nrow(forecast_data2)) {
  forecast_data2$e_values[i] <- E_p_0 [i]*0+E_p_1 [i]*ifelse(random_amounts_1[i] > forecast_data2$nb_excess[i],0.92*(random_amounts_1[i] - forecast_data2$nb_excess[i] / 1.1) * forecast_data2$nb_contribution[i] / 100,0) + E_p_2 [i]*ifelse(random_amounts_1[i] > forecast_data2$nb_excess[i],0.92*(random_amounts_1[i] - forecast_data2$nb_excess[i] / 1.1) * forecast_data2$nb_contribution[i] / 100+0.92*random_amounts_2[i] * forecast_data2$nb_contribution[i] / 100,ifelse(random_amounts_2[i] > forecast_data2$nb_excess[i],0.92*(random_amounts_2[i] - forecast_data2$nb_excess[i] / 1.1) * forecast_data2$nb_contribution[i] / 100,0))
}
sum(lambda0*random_amounts_1)
sum(forecast_data2$e_values)
forecast_data<- forecast_data[!forecast_data$nb_breed_trait %in% c('siamese', 'forest cat', 'spotted cats', 'persian', 'burmese'), ]
merged_data <- forecast_data %>%
  mutate(Full_month_premium=forecast_data2$e_values)
write.csv(merged_data, "output_5305.csv", row.names = FALSE)
```



